\documentclass[a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}


\usepackage{etoolbox}
\input{glyphtounicode}

\emergencystretch=3em

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
  {#1 \vspace{-2pt}}
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingc}[8]{
\noindent
\begin{minipage}[c]{0.5\linewidth}
  \vspace{-1pt}\item
    \begin{tabular*}{0.3\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
    \end{minipage}\begin{minipage}[c]{0.5\linewidth}
      \vspace{-1pt}\item 
    \begin{tabular*}{0.3\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#5} & #6 \\
      \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-5pt}\end{minipage}
}

\newcommand{\resumeSubheadingb}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \vspace{-3pt}
      \textbf{#1} & #2 \\
         \textit{\scriptsize(#3)} & \textit{\scriptsize #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPro}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\textit {\small{#2}}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProb}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\textit {\small{#2}}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPOR}[2]{
 \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{   #1} & #2 
    \end{tabular*}
  \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeProject}[3]{
    \item \textbf{#1} $|$ \emph{#2} $|$ \href{#3}{\faIcon{external-link-alt}}
}

\newlist{resumeSubHeadingList}{itemize}{1}
\setlist[resumeSubHeadingList]{label={}, leftmargin=0.15in, rightmargin=0.15in}
%------------------------

\begin{document}

\begin{center}
    \textbf{\Huge Samminga Sainath Rao} \\
    \small \faPhone\ +918331098232 ~ \faEnvelope\ \href{mailto:sammingasainathrao@gmail.com}{sammingasainathrao@gmail.com} ~ 
    \faLinkedin\ \href{https://www.linkedin.com/in/samminga}{linkedin.com/in/samminga} ~ 
    \faGithub\ \href{https://github.com/sammingasainath}{github.com/sammingasainath}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\begin{resumeSubHeadingList}
    \resumeSubheading
    {B.Tech in CSE and M.Tech in Artificial Intelligence}{2021 -- Present}
    {Rajiv Gandhi Institute of Petroleum Technology (RGIPT), Jais}{CPI: 8.52/10}
    \resumeSubheading
    {APBIE: Intermediate}{2020}
    {Andhra Pradesh Board}{Percentage: 95.7\%}
    \resumeSubheading
    {JEE Advanced}{2021}
    {Qualified}{}
\end{resumeSubHeadingList}

%-----------EXPERIENCE-----------
\section{Experience}
\begin{resumeSubHeadingList}
    \resumeSubheading
    {Solvitarka Solutions Pvt Ltd}{May 2024 -- Oct 2024}
    {Fullstack Development Intern (\href{https://sai.fhaida.com/\#experience-2}{Media})}{Work From Home}
    \begin{itemize}[label={\small$\bullet$}, itemsep=-2pt]
        \item Developed and optimized full-stack applications using React, React Native, and Next.js, focusing on creating responsive SPAs and mobile apps.
        \item Integrated backend server APIs, managed application state, and collaborated on UI/UX design refinements.
        \item Gained hands-on experience in fine-tuning and implementing Large Language Models (LLMs) for specialized tasks.
    \end{itemize}

    \resumeSubheading
    {Sambin Technologies Private Limited}{Apr 2024 -- Present}
    {Cofounder | Software Engineer \& Product Manager (\href{https://sai.fhaida.com/\#experience-1}{Media})}{Visakhapatnam, India}
    \begin{itemize}[label={\small$\bullet$}, itemsep=-2pt]
        \item Architected scalable systems, managed the full product lifecycle, and led a team of 7 interns.
        \item Drove market research, devised marketing strategies, and handled legal compliance for a NASSCOM-funded startup.
        \item Spearheaded a voice-based billing software project, integrating an Appwrite backend and a voice assistant.
    \end{itemize}
\end{resumeSubHeadingList}

%-----------PROJECTS-----------
\section{Projects}
\begin{resumeSubHeadingList}
    \resumeProject{Voice-Based AI Assistant for Small Indian Retailers}{Flutter, Firebase, On-device LLM}{https://sai.fhaida.com/\#project-1}
    \resumeProject{User-Friendly CRM for Real Estate Agents}{Flutter, Firebase, Node.js, AWS}{https://sai.fhaida.com/\#project-2}
    \resumeProject{DishDash: Fitness Fueler \& Budget Buddy}{Flutter, Google OR-Tools, REST API}{https://sai.fhaida.com/\#project-3}
    \resumeProject{Serverless UPI Payment Confirmation System}{Flutter, Background Services}{https://sai.fhaida.com/\#project-4}
    \resumeProject{Post4Planet: Transforming Indian Postal Services}{Flutter, Firebase, AI, QR Systems}{https://sai.fhaida.com/\#project-5}
    \resumeProject{Anu Civil - GeoExploratory Project Management}{Next.js, Flutter, Firebase}{https://sai.fhaida.com/\#project-6}
    \resumeProject{Harit Parishar - Sustainability Empowerment App}{Flutter, Firebase, ML Kit, TensorFlow}{https://sai.fhaida.com/\#project-7}
    \resumeProject{Institute Gate Management (QR Code System)}{Google Apps Script, Flutter, Django}{https://sai.fhaida.com/\#project-8}
    \resumeProject{Unified Workplace Data System}{Google Apps Script, Webhooks, Chrome Extension}{https://sai.fhaida.com/\#project-10}
    \resumeProject{Gaze-Controlled Video Player (Blink-to-Pause)}{Python, OpenCV, PyAutoGUI}{https://sai.fhaida.com/\#project-12}
    \resumeProject{Retrieval-Augmented Assessment Recommender}{FastAPI, Streamlit, Supabase, Gemini}{https://sai.fhaida.com/\#project-14}
    \resumeProject{Ultimate College Ranking Engine}{Next.js, FastAPI, NSGA-II}{https://sai.fhaida.com/\#project-18}
\end{resumeSubHeadingList}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{resumeSubHeadingList}
    \item{\textbf{NASSCOM Foundation's ThingQbator:} Top 10 Finalist; Project \textbf{AMYR} secured \textbf{Rs. 5 Lakh Seed Grant Funding} and mentorship. (\href{https://sai.fhaida.com/\#achievement-1}{Media})}
    \item{Won \textbf{1st Prize} in the \textbf{UDAAN 2023} Business Plan Competition (Rs. 25,000). (\href{https://sai.fhaida.com/\#achievement-2}{Media})}
    \item{Winner of \textbf{Smart India Hackathon 2024} (Rs. 1 Lakh) for the \textbf{ESG Post Office Initiative}. (\href{https://sai.fhaida.com/\#achievement-3}{Media})}
    \item{\textbf{Digital Marketing Manager at Aastee.com:} Generated 900+ leads via YouTube campaigns. (\href{https://sai.fhaida.com/\#achievement-4}{Media})}
    \item{Won \textbf{1st Prize} at the \textbf{Codeiam Hackathon 2024} for "Smart CRM System in Google Sheets". (\href{https://sai.fhaida.com/\#achievement-5}{Media})}
    \item{Finalist in multiple national and international hackathons. (\href{https://sai.fhaida.com/\#achievement-6}{Media})}
\end{resumeSubHeadingList}

%-----------SKILLS-----------
\section{Skills}
\begin{multicols}{3}
    \begin{resumeSubHeadingList}
        \resumeSubItem{Languages}{Java, C++, Python, Dart, JavaScript, SQL, HTML/CSS}
        \resumeSubItem{Frontend}{React, React Native, Flutter, Next.js, Tailwind CSS}
        \resumeSubItem{Backend}{Node.js, Django, Flask, Appwrite, Google Apps Script}
        \resumeSubItem{Databases \& Cloud}{MongoDB, Firebase, SQLite, AWS, Docker}
        \resumeSubItem{AI/ML}{TensorFlow, PyTorch, LLM Fine-tuning, RAG, OCR, CV}
        \resumeSubItem{Design \& Media}{Blender, Maya, Adobe Suite (PS, AI, AE), UI/UX}
        \resumeSubItem{Business}{Product Management, Digital Marketing, SEO, Research}
        \resumeSubItem{Core Concepts}{Data Structures, Algorithms, OOP, DBMS, Networks}
        \resumeSubItem{Soft Skills}{Leadership, Team Mentorship, Problem Solving}
    \end{resumeSubHeadingList}
\end{multicols}

%-----------EXTRA-CURRICULAR-----------
\section{Leadership \& Volunteering}
\begin{resumeSubHeadingList}
    \item{\textbf{General Secretary}, Science and Technical Council, RGIPT (2023-2024): Led technical initiatives and events. (\href{https://sai.fhaida.com/\#leadership-1}{Media})}
    \item{\textbf{President}, ThingQbator Student Body, RGIPT (2022-2023): Headed innovation program, mentoring students. (\href{https://sai.fhaida.com/\#leadership-2}{Media})}
    \item{\textbf{Active Member} in Entrepreneurship Cell, ACM, and CodeChef student chapters. (\href{https://sai.fhaida.com/\#leadership-3}{Media})}
    \item{\textbf{Volunteer Teacher} for the Gyanapran Program, teaching STEM to rural students. (\href{https://sai.fhaida.com/\#volunteer-1}{Media})}
\end{resumeSubHeadingList}

\end{document} 